---
title: "p8105_hw1_ver2117"
author: "Varvy Rousseau"
date: "2022-09-20"
output: github_document
---
```{r}
# Problem 1

data("penguins", package = "palmerpenguins")
summary(penguins)

mean(penguins$bill_length_mm, na.rm = TRUE)


```

The data contains the species of penguins, the island where they are from and their bill depth, length, flipper length, sex, and the year

The species(Adelie, Chinstrap, Gentoo) found in the penguins dataset is `r penguins$species`

The islands(Biscoe, Dream, Torgersen) found in the penguins dataset is `r penguins$island`

The mean(43.92mm) of bill length in mm found in the penguins dataset is `r mean(penguins$ bill_length_mm, na.rm = TRUE)`

The mean(17.15mm) of bill depth in mm found in the penguins dataset is `r mean(penguins$ bill_depth_mm, na.rm = TRUE)`

The mean(200.9 mm) of flipper length in mm found in the penguins dataset is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`

The mean(4202 g) of body mass of the penguins dataset is `r mean(penguins$body_mass_g, na.rm = TRUE)`

The number of rows in the penguins dataset is `r nrow(penguins)`
The number of columns in the penguins dataset is `r ncol(penguins)`

```{r}
library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = species))

ggsave("Rplot.png")

```


## Problem 2





