---
title: "p8105_hw1_ver2117"
author: "Varvy Rousseau"
date: "2022-09-20"
output: github_document
---

```{r}
#Loading in relevant packages for project
library(tidyverse)
```



```{r}
# Problem 1
#Used this code to download the data set penguins
data("penguins", package = "palmerpenguins")

#Getting a summary of descriptive statistics of variables 
summary(penguins)


#Getting the mean using the pull function to pull the variable out of the dataframe; this is for the mean of bill length of penguins

mean(pull(penguins, bill_length_mm), na.rm = TRUE)

```

The data contains the species of penguins, the island where they are from and their bill depth, length, flipper length, sex, and the year

The species(Adelie, Chinstrap, Gentoo) found in the penguins dataset is `r pull(penguins, species)`

The islands(Biscoe, Dream, Torgersen) found in the penguins dataset is `r pull(penguins, island)`

The mean(43.92mm) of bill length in mm found in the penguins dataset is `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)`

The mean(17.15mm) of bill depth in mm found in the penguins dataset is `r mean(pull(penguins, bill_depth_mm), na.rm = TRUE)`

The mean(200.9 mm) of flipper length in mm found in the penguins dataset is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

The mean(4202 g) of body mass of the penguins dataset is `r mean(pull(penguins, body_mass_g), na.rm = TRUE)`

The number of rows in the penguins dataset is `r nrow(penguins)`
The number of columns in the penguins dataset is `r ncol(penguins)`

```{r}
library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = species))

ggsave("Rplot.png")

```


## Problem 2

```{r}
prob2_df= tibble(
  r_sample = rnorm(10),
  vec_logical = r_sample > 0,
  vec_char = c("z", "y", "x", "w", "v", "u", "t", "s", "r","q"),
  vec_factor = factor(c("large", "medium","small", "large", "medium", "small", "large", "medium", "small", "large"), levels = c("small", "medium", "large"))
  )

```



```{r}

# finding the mean of my data frame that I created using the mean and pull function of each variable

mean(pull(prob2_df, r_sample))

mean(pull(prob2_df, vec_logical))

mean(pull(prob2_df, vec_char))

mean(pull(prob2_df, vec_factor))

```

When trying to take the mean of each variable in my data frame, the mean of the random sample is computed as `r mean(pull(prob2_df, r_sample))`

The mean of the logical vector is computed as `mean(pull(prob2_df, vec_logical))`

The character vector cannot be computed as `mean(pull(prob2_df, vec_char))`

The factor vector cannot be computed as `mean(pull(prob2_df, vec_factor))`

```{r}
#converting the logical, character and factor vector into numbers using the as.numeric function
as.numeric(pull(prob2_df, r_sample))

as.numeric(pull(prob2_df, vec_logical))

as.numeric(pull(prob2_df, vec_char))

as.numeric(pull(prob2_df, vec_factor))

```

After using `as.numeric(pull(prob2_df, vec_logical))`for the logical vector the value of 0) is assigned to False and the value of 1 is assigned to True. This allows us to interpret the logical vector in a proportional sense.   

When using the `as.numeric(pull(prob2_df, vec_char))`for the character vector it converts the values to NA because it is not a logical or numeric variabe which is the same for mean. It helps us show that this is true. 

I also used `as.numeric(pull(prob2_df, vec_factor))`for the factor variable and it converted the levels into numbers 1,2, or 3 after I assigned these levels a specific order. Previously, before I tried to take the mean of the factor variable, R gave me a warning because the differences between large and medium or large and small could not be defined. So when I change the factor variable and levels to numbers, now I can compute the mean. 





